### 2018-06-20 paper/5-implementations.tex
Bit at the start of 5

In the previous sections we discussed the types of build systems, and how they
can be broken down into two main components: a scheduler and a rebuilder. This
decomposition was not obvious to us, and only by concretely implementing and
refactoring each build system did we determine the underlying commonalities.
In this section we share some of the code that got us there.

>>>>

In the previous sections we discussed the types of build systems, and how they
can be broken down into two main components: a scheduler and a rebuilder.
In this section we make this abstract distinction concrete, by actually
implementing a number of build systems as a composition of a schedulear
and a rebuilder.  Our design is expressed by these types:
\begin{minted}[xleftmargin=10pt]{haskell}
type Scheduler c i k v = Rebuilder c i k v -> Build c k v
type Rebuilder c i k v = k -> v -> Task c k v -> Task (MonadState i) k v
\end{minted}
That is:
\begin{itemize}
\item A \hs{Scheduler} is just a function that takes a \hs{Rebuilder} and uses
  it to construct \hs{Build} system, by choosing which keys to rebuild in which order.
\item A \hs{Rebuilder} is a function that is given a key, the key's ``old'' value,
  and a \hs{Task} that can compute the value of the key if necessary. It uses
  the persistent build state \hs{i} (carried by the state monad) to decide
  whether to re-build the value.  If doing so is unnecesary, it returns the
  old value; otherwise it runs the supplied \hs{Task} to rebuild it.  In both
  cases it updates the persistent build information \hs{i} to reflect what happened.
\end{itemize}
